Utilizing Convolution for Obstacle Avoidance during Robotic Manipulator Movement

### 2023-07-24 Articles/ERK/erk.tex
ERK equations format
fixed constants
ERK todocomments
ERK plots
ERK more plots 7-DOF_Robot_Positions_Standard_vs_Avoidance.eps

\todocomment{IMAGE OF ROBOT}

@@

@@

@@

\[
C_d = A_d \odot K_d
\]

@@

\[
v = \sum_{i}\sum_{j}\sum_{k} a_{ijk} 
\]

@@

\subsection{Kernel Convolution}

@@

\todocomment{add element-wise convolution equation}

@@

@@

\todocomment{- The wall visualization with robot and wall and "dy beam" and dy arrow. \\
			 - Line field strenght 2D plot dx,dy,dz \\
		 	 - }

\section{Pisanje prispevka}

Pri pisanju uporabljajte sloge, ki so definirani v datoteki erk.sty in ne spreminjajte velikosti ali sloga pisave. Ta dokument lahko vzamete kot vzorec za oblikovanje prispevka v orodju \LaTeX.
Tabela \ref{tab1} povzema osnovne sloge in velikosti pisave.

\begin{table}[h]
\caption{Osnovni slogi pri oblikovanju prispevka.} \label{tab1}
\smallskip
\begin{center}
\begin{tabular}{ | r | c | c | }
\hline  
  \textbf{Text Style} & \textbf{Font Size} & \textbf{Attributes}\\ 
\hline  
  Paper title & 17pt & bold\\
  Author names & 12pt & bold\\
  Affiliation & 10pt & italic\\
  Heading & 12pt & bold \\
  Subheading & 10pt & bold\\
  Regular text & 10pt &\\
  Captions \& ref. & 9pt &\\
\hline  
\end{tabular}
\end{center}
\end{table}

\subsection{Enačbe in slike}

Enačbe in formule se pišejo s poševnimi črkami in so zaporedno oštevilčene. V besedilu naj bodo reference na enačbe zapisane v oklepajih (\ref{eq1}).

\begin{equation}
 \int^{r_{2}}_{0}F(r,\varphi)\; dr\; d\varphi= [\sigma r_{2} / (2\mu_{0})]
    \label{eq1}
\end{equation}

Prispevki za ERK se ne tiskajo v barvah, zato pripravite črno-bele slike. Slike naj bodo postavljene v okvirje širine enega ali dveh stolpcev in označene s številko in podnapisom. V besedilu morajo biti reference na slike (slika \ref{slika}).

\begin{figure}[!htb]
    \begin{center}
        \includegraphics[scale=1]{field1.eps}
        \caption{Podajte kratko razlago slike.} \label{slika}
    \end{center}
\end{figure}

\section{Oddaja prispevka}

Prispevek oddajte v elektronski obliki preko formularja na spletni strani \cite{ERK}. Sprejemamo prispevke v formatu pdf (brez nastavljenih zaščitnih gesel) ali Microsoft Word. Pred oddajo prispevka prosimo preverite dodatne informacije za avtorje, ki so na spletnih straneh.

Formular za elektronsko oddajo prispevkov bo aktiviran v juniju, rok za oddajo je \textbf{13. julij 2014}. Avtorje bomo obvestili o izboru konec avgusta.

>>>>

\todocomment{IMAGE OF THE TASK}

@@

\todocomment{check if "exact equation" gives better results}

@@

\todocomment{želena sredinska lega sklepov}

@@

\begin{equation}
	C_d = A_d \odot K_d
	\label{eq:hadamard}
\end{equation}

@@

\begin{equation}
v = \sum_{i}\sum_{j}\sum_{k} a_{ijk} 
\label{summation}
\end{equation}

@@

\subsection{Convolution Kernel}

@@

@@

In our end-effector motion planning approach, we leverage derivatives of the attractive field to facilitate efficient trajectory generation. Prior to commencing motion planning, we construct a distance matrix, analogous in size to the matrix representing the obstacles. This distance matrix encompasses distance values from our designated goal point, corresponding to each voxel in the workspace. Subsequently, we employ interpolation techniques to estimate the value at the current end-effector (EE) point by considering the distance field values of the eight neighboring voxels and the distances of the current EE pose relative to these eight values. By performing interpolation between two points, we effectively calculate the numerical derivative of distance change, thereby obtaining the EE velocity. This approach enables us to navigate the robotic manipulator smoothly towards the desired goal while considering the surrounding obstacle space.

Additionally, we can augment our velocity component with repulsive fields, which are calculated using the convolutional kernel technique. This enables us to guide the end-effector around obstacles smoothly, ensuring safe and collision-free navigation while dynamically adapting to the environment. By integrating both the attractive and repulsive field contributions, our motion planning approach ensures efficient and effective trajectory generation, enabling the robotic manipulator to reach its desired goal while avoiding potential obstacles in the workspace.

@@

\todocomment{- The wall visualization with robot and wall and "dy beam" and dy arrow. \\
				(with and without avoidance 3 to 5 keypoints) \\
		 	  }

\begin{figure}[htbp]
	\centering
	\includegraphics[width=1.0\linewidth]{Repulsive-Velocities-Along-the-Y-Axis-wide.eps}
	\caption{Repulsive Velocities Along the Y Axis}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=1.0\linewidth]{Y-Positions.eps}
	\caption{Repulsive Velocities Along the Y Axis}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=1.0\linewidth]{7-DOF_Robot_Positions_Standard_vs_Avoidance.eps}
	\caption{Repulsive Velocities Along the Y Axis}
\end{figure}

\todocomment{Maybe add joint positions plot, however might me too much}

\section{Conclusions and further development}

\todocomment{ADD}
